Jager: Symbolic Specification-Based Program Adjustment

### 2013-05-01 paper/paper.tex
Finishing up a paragraph in the future work section and adding notes for other items to discuss.

With respect to the trace generation phase, we are interested in exploring
ways in which less traces need to be generated. Our approach exhaustively
generates all traces for a program. While this may be feasible for the small
programs we have worked with, it could quickly becoming intractable for even
medium-sized programs. Existing program repair approaches do not suffer from
this kind of problem because they generate traces from test suites which
remain resonable in size even for large projects. It would be interesting to
see if there is some sweet spot sitting between the set of \emph{all} traces
through a program and the set of traces generated from a test suite.
Ideally, this sweet spot would be less computationally intensive than
generating all traces, but still provide better behavior coverage than a
traditional test suite.

During the trace differentiation phase and fault localization phase, we
identify \emph{good} and \emph{bad} traces and use them to localize faulty
program statements. In approaches that generate traces from test suites, we
can be reasonably sure that the traces represent interesting and relevant
paths through the program based on common use cases. However, with our
approach, we generate all traces, some of which may not be common or
interesting. Because of this, we believe it may be useful to consider ways
of weighting certain paths through the program

>>>>

With respect to the trace generation phase, we are interested in exploring
ways in which less traces need to be generated. Our approach exhaustively
generates all traces for a program. While this may be feasible for the small
programs we have worked with, it could quickly becoming intractable for even
medium-sized programs. Existing program repair approaches do not suffer from
this kind of problem because they generate traces from test suites which
remain reasonable in size even for large projects. It would be interesting to
see if there is some sweet spot sitting between the set of \emph{all} traces
through a program and the set of traces generated from a test suite.
Ideally, this sweet spot would be less computationally intensive than
generating all traces, but still provide better behavior coverage than a
traditional test suite.

During the trace differentiation phase and fault localization phase, we
identify \emph{good} and \emph{bad} traces and use them to localize faulty
program statements. In approaches that generate traces from test suites, we
can be reasonably sure that the traces represent interesting and relevant
paths through the program based on common use cases. However, with our
approach, we generate all traces, some of which may not be common or
interesting. Because of this, we believe it may be useful to consider ways
of weighting certain paths through the program. It is unclear at this point
how we would go about weighting certain traces over others though.

Generate more succinct constraints for the synthesis...

Add more complex grammars to the synthesis...
